Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-05-29 main.tex
Fixed writing to account for new figure.

\begin{figure} 
\centering
\includegraphics[width=3.4in]{figures/speedVsResolution}
\caption{Recognition stage runtime vs. size of training database.}
\label{fig:recognition_stage_runtime} \end{figure}

Finally, we perform an experiment verifying the recognition accuracy of the
overall pipeline.  Since one would expect higher recognition rates but longer
execution time for higher resolution images, we compare the recognition rate of
the overall pipeline with the face recognition stage run at 5 different
canonical image resolutions: $32\times32, 48 \times 48, 64 \times 64, 96 \times
96, \textrm{and} 128 \times 128$.  As motivated by Figure
\ref{fig:user_alignment_rank_plot}, we fix the number of gallery users to 20,
giving approximately 95\% probability to have the true user in the training
set.  
%The inner loop tolerance to 1e-5 and outer loop tolerance to 1e-2.  
\begin{figure}
\centering
\includegraphics[width=3.4in]{figures/accuracyVsResolution}
\caption{Recognition rate of the full pipeline vs. face window resolution.}
\label{fig:accuracy_vs_resolution}
\end{figure}
As can be seen in Figure \ref{fig:accuracy_vs_resolution}, at the optimal
resolution, which happens to match the alignment stage resolution, this bound
is very nearly achieved by the GPU implementation.  For significantly lower
resolutions, the accuracy drops off significantly.  Of the two main stages of
the face recognition pipeline, the iterative alignment stage is by far the most
expensive; the recognition stage requires less than one second.

>>>>

The next experiment compares the speed of the GPU and CPU implementations of
the recognition stage.  It was determined that keeping 20 gallery users is
sufficient to ensure that the correct user is kept for the recognition stage
with 95\% probability.  Since recognition failures are typically caused by a
poor alignment, we find that keeping more users for the recognition stage does
not necessarily improve recognition rate.
%The inner loop tolerance to 1e-5 and outer loop tolerance to 1e-2.  
In Figure \ref{fig:recognition_stage_runtime} we show recognition stage runtime
for canonical images of size: $32\times32$, $48 \times 48$, $64 \times 64$, $96 \times
96$, and $128 \times 128$.  For all image resolutions the problem size
is sufficiently small that the CPU is significantly faster than the GPU.  Note
also that for both implementations, the recognition stage takes much less time
than the alignment stage.
\begin{figure} 
\centering
\includegraphics[width=3.4in]{figures/speedVsResolution}
\caption{Recognition stage runtime vs. size of training database.}
\label{fig:recognition_stage_runtime} \end{figure}

\begin{figure}
\centering
\includegraphics[width=3.4in]{figures/accuracyVsResolution}
\caption{Recognition rate of the full pipeline vs. face window resolution.}
\label{fig:accuracy_vs_resolution}
\end{figure}
Finally, we perform an experiment verifying the recognition accuracy of the
overall pipeline.  As can be seen in Figure \ref{fig:accuracy_vs_resolution},
at the optimal resolution, which happens to match the alignment stage
resolution, the GPU implementation reaches 95\% recognition rate, the max
achievable given the alignment results.  For significantly lower resolutions,
the accuracy drops off significantly.
